New lower bounds for Schur and weak Schur numbers

### 2021-05-04 article/weakschur.tex
Application identité

Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
\[ \pi_{a,b}:x \longmapsto (Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)\]
\end{definition}

@@

\[
\begin{array}{c c l l}
	\pi(x+y) & = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a) & \\
	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a) & \text{since } \pi(y)=y \mod a \\
	& = & x+ \pi(y) &
\end{array}
\]

\noindent if \(x+\pi(y)\geqslant a\):
\[
\begin{array}{c c l l}
	\pi(x+y) & = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)& \\
	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a) & \text{since } \pi(y)=y \mod a \\
	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) & \\
	& = & x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]}(x+\pi(y) - a) & \\
	& = & x+\pi(y) - a +a & \text{since } x+\pi(y) - a \in [\![0,b]\!] \\
	& = & x+\pi(y) &
\end{array}
\]
\end{proof}

@@

\[
\begin{array}{c c l}
	\pi(\pi(x)+\pi(y)) & = & (Id+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a) \mod a) \\
	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
	& = & (Id+a\mathds{1}_{ [\![0,b]\!]})( x+y \mod a)\\
	& = & \pi(x+y)
\end{array}
\]
\end{proof}

>>>>

Let \((a,b) \in (\mathbb{N}^*)^2\) such that \(a>b\). Define
\[ \pi_{a,b}:x \longmapsto (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)\]
\end{definition}

@@

\[
\begin{array}{c c l l}
	\pi(x+y) & = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a) & \\
	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) \mod a) & \text{since } \pi(y)=y \mod a \\
	& = & x+ \pi(y) &
\end{array}
\]

\noindent if \(x+\pi(y)\geqslant a\):
\[
\begin{array}{c c l l}
	\pi(x+y) & = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+y \mod a)& \\
	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y)\mod a) & \text{since } \pi(y)=y \mod a \\
	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(x+\pi(y) - a) & \\
	& = & x+\pi(y) - a +a\mathds{1}_{ [\![0,b]\!]}(x+\pi(y) - a) & \\
	& = & x+\pi(y) - a +a & \text{since } x+\pi(y) - a \in [\![0,b]\!] \\
	& = & x+\pi(y) &
\end{array}
\]
\end{proof}

@@

\[
\begin{array}{c c l}
	\pi(\pi(x)+\pi(y)) & = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(\pi(x)+\pi(y) \mod a)\\
	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})((Id+a\mathds{1}_{ [\![0,b]\!]})(x \mod a)+(Id+a\mathds{1}_{ [\![0,b]\!]})(y \mod a) \mod a) \\
	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})(((x \mod a) + (y \mod a)) \mod a)\\
	& = & (\operatorname{Id}+a\mathds{1}_{ [\![0,b]\!]})( x+y \mod a)\\
	& = & \pi(x+y)
\end{array}
\]
\end{proof}
